---
title: "Calculating Correlation Between Mutation Operators"
author: "Beatriz Souza"
date: "6/1/2019"
output: html_document
---

## Installing and loading packages
```{r}
install.packages("ggpubr")
install.packages("ggplot2")
install.packages("reshape2")
library("ggplot2")
library("reshape2")
library("ggpubr")
```

## Reading data
```{r}
evoResults1 <- read.csv('/home/beatriz/Desktop/pibicDataSet/evoResults.csv', sep = ",", header = TRUE)
evoResults2 <- read.csv('/home/beatriz/Desktop/pibicDataSet/evoResults2.csv', sep = ",", header = TRUE)
evoResults3 <- read.csv('/home/beatriz/Desktop/pibicDataSet/evoResults3.csv', sep = ",", header = TRUE)

randoopResults1 <- read.csv('/home/beatriz/Desktop/pibicDataSet/randoopResults.csv', sep = ",", header = TRUE)
randoopResults2 <- read.csv('/home/beatriz/Desktop/pibicDataSet/randoopResults2.csv', sep = ",", header = TRUE)
randoopResults3 <- read.csv('/home/beatriz/Desktop/pibicDataSet/randoopResults3.csv', sep = ",", header = TRUE)

manualResults1 <- read.csv('/home/beatriz/Desktop/pibicDataSet/manualSuitesResults.csv', sep = ",", header = TRUE)
manualResults2 <- read.csv('/home/beatriz/Desktop/pibicDataSet/manualSuitesResults2.csv', sep = ",", header = TRUE)
manualResults3 <- read.csv('/home/beatriz/Desktop/pibicDataSet/manualSuitesResults3.csv', sep = ",", header = TRUE)
```

## Merging data
```{r}
evoResults12 <- merge(evoResults1, evoResults2, all = TRUE)
#evo12
evoResults123 <- merge(evoResults12, evoResults3, all = TRUE)
#evoResults123

randoopResults12 <- merge(randoopResults1, randoopResults2, all = TRUE)
#randoopResults12
randoopResults123 <- merge(randoopResults12, randoopResults3, all = TRUE)
#randoopResults123

manualResults12 <- merge(manualResults1, manualResults2, all = TRUE)
#manualResults12
manualResults123 <- merge(manualResults12, manualResults3, all = TRUE)
#manualResults123

evoAndRandoopDataSet <- merge(evoResults123, randoopResults123, all = TRUE)
completeDataSet <- merge(evoAndRandoopDataSet, manualResults123, all = TRUE)
#completeDataSet
```

## ReturnValsMutator

# ReturnValsMutator vs ConditionalsBoundaryMutator
```{r}
par(mfrow = c(2,2))
plot(evoResults123$ConditionalsBoundaryMutator ~ evoResults123$ReturnValsMutator, data = evoResults123)
plot(randoopResults123$ConditionalsBoundaryMutator ~ randoopResults123$ReturnValsMutator, data = randoopResults123)
plot(manualResults123$ConditionalsBoundaryMutator ~ manualResults123$ReturnValsMutator, data = manualResults123)

cor.test(evoResults123$ConditionalsBoundaryMutator, evoResults123$ReturnValsMutator, method='spearman')
cor.test(randoopResults123$ConditionalsBoundaryMutator, randoopResults123$ReturnValsMutator, method='spearman')
cor.test(manualResults123$ConditionalsBoundaryMutator, manualResults123$ReturnValsMutator, method='spearman')
```

# ReturnValsMutator vs VoidMethodCallMutator
```{r}
par(mfrow = c(2,2))
plot(evoResults123$VoidMethodCallMutator ~ evoResults123$ReturnValsMutator, data = evoResults123)
plot(randoopResults123$VoidMethodCallMutator ~ randoopResults123$ReturnValsMutator, data = randoopResults123)
plot(manualResults123$VoidMethodCallMutator ~ manualResults123$ReturnValsMutator, data = manualResults123)

cor.test(evoResults123$VoidMethodCallMutator, evoResults123$ReturnValsMutator, method='spearman')
cor.test(randoopResults123$VoidMethodCallMutator, randoopResults123$ReturnValsMutator, method='spearman')
cor.test(manualResults123$VoidMethodCallMutator, manualResults123$ReturnValsMutator, method='spearman')
```

# ReturnValsMutator vs IncrementsMutator
```{r}
par(mfrow = c(2,2))
plot(evoResults123$IncrementsMutator ~ evoResults123$ReturnValsMutator, data = evoResults123)
plot(randoopResults123$IncrementsMutator ~ randoopResults123$ReturnValsMutator, data = randoopResults123)
plot(manualResults123$IncrementsMutator ~ manualResults123$ReturnValsMutator, data = manualResults123)

cor.test(evoResults123$IncrementsMutator, evoResults123$ReturnValsMutator, method='spearman')
cor.test(randoopResults123$IncrementsMutator, randoopResults123$ReturnValsMutator, method='spearman')
cor.test(manualResults123$IncrementsMutator, manualResults123$ReturnValsMutator, method='spearman')
```

# ReturnValsMutator vs NegateConditionalsMutator
```{r}
par(mfrow = c(2,2))
plot(evoResults123$NegateConditionalsMutator ~ evoResults123$ReturnValsMutator, data = evoResults123)
plot(randoopResults123$NegateConditionalsMutator ~ randoopResults123$ReturnValsMutator, data = randoopResults123)
plot(manualResults123$NegateConditionalsMutator ~ manualResults123$ReturnValsMutator, data = manualResults123)

cor.test(evoResults123$NegateConditionalsMutator, evoResults123$ReturnValsMutator, method='spearman')
cor.test(randoopResults123$NegateConditionalsMutator, randoopResults123$ReturnValsMutator, method='spearman')
cor.test(manualResults123$NegateConditionalsMutator, manualResults123$ReturnValsMutator, method='spearman')
```

# ReturnValsMutator vs MathMutator
```{r}
par(mfrow = c(2,2))
plot(evoResults123$MathMutator ~ evoResults123$ReturnValsMutator, data = evoResults123)
plot(randoopResults123$MathMutator ~ randoopResults123$ReturnValsMutator, data = randoopResults123)
plot(manualResults123$MathMutator ~ manualResults123$ReturnValsMutator, data = manualResults123)

cor.test(evoResults123$MathMutator, evoResults123$ReturnValsMutator, method='spearman')
cor.test(randoopResults123$MathMutator, randoopResults123$ReturnValsMutator, method='spearman')
cor.test(manualResults123$MathMutator, manualResults123$ReturnValsMutator, method='spearman')
```

# ReturnValsMutator vs InvertNegsMutator
```{r}
par(mfrow = c(2,2))
plot(evoResults123$InvertNegsMutator ~ evoResults123$ReturnValsMutator, data = evoResults123)
plot(randoopResults123$InvertNegsMutator ~ randoopResults123$ReturnValsMutator, data = randoopResults123)
plot(manualResults123$InvertNegsMutator ~ manualResults123$ReturnValsMutator, data = manualResults123)

cor.test(evoResults123$InvertNegsMutator, evoResults123$ReturnValsMutator, method='spearman')
cor.test(randoopResults123$InvertNegsMutator, randoopResults123$ReturnValsMutator, method='spearman')
cor.test(manualResults123$InvertNegsMutator, manualResults123$ReturnValsMutator, method='spearman')
```

## ConditionalsBoundaryMutator

# ConditionalsBoundaryMutator vs VoidMethodCallMutator
```{r}
par(mfrow = c(2,2))
plot(evoResults123$VoidMethodCallMutator ~ evoResults123$ConditionalsBoundaryMutator, data = evoResults123)
plot(randoopResults123$VoidMethodCallMutator ~ randoopResults123$ConditionalsBoundaryMutator, data = randoopResults123)
plot(manualResults123$VoidMethodCallMutator ~ manualResults123$ConditionalsBoundaryMutator, data = manualResults123)

cor.test(evoResults123$VoidMethodCallMutator, evoResults123$ConditionalsBoundaryMutator, method='spearman')
cor.test(randoopResults123$VoidMethodCallMutator, randoopResults123$ConditionalsBoundaryMutator, method='spearman')
cor.test(manualResults123$VoidMethodCallMutator, manualResults123$ConditionalsBoundaryMutator, method='spearman')
```

# ConditionalsBoundaryMutator vs IncrementsMutator
```{r}
par(mfrow = c(2,2))
plot(evoResults123$IncrementsMutator ~ evoResults123$ConditionalsBoundaryMutator, data = evoResults123)
plot(randoopResults123$IncrementsMutator ~ randoopResults123$ConditionalsBoundaryMutator, data = randoopResults123)
plot(manualResults123$IncrementsMutator ~ manualResults123$ConditionalsBoundaryMutator, data = manualResults123)

cor.test(evoResults123$IncrementsMutator, evoResults123$ConditionalsBoundaryMutator, method='spearman')
cor.test(randoopResults123$IncrementsMutator, randoopResults123$ConditionalsBoundaryMutator, method='spearman')
cor.test(manualResults123$IncrementsMutator, manualResults123$ConditionalsBoundaryMutator, method='spearman')
```

# ConditionalsBoundaryMutator vs NegateConditionalsMutator
```{r}
par(mfrow = c(2,2))
plot(evoResults123$NegateConditionalsMutator ~ evoResults123$ConditionalsBoundaryMutator, data = evoResults123)
plot(randoopResults123$NegateConditionalsMutator ~ randoopResults123$ConditionalsBoundaryMutator, data = randoopResults123)
plot(manualResults123$NegateConditionalsMutator ~ manualResults123$ConditionalsBoundaryMutator, data = manualResults123)

cor.test(evoResults123$NegateConditionalsMutator, evoResults123$ConditionalsBoundaryMutator, method='spearman')
cor.test(randoopResults123$NegateConditionalsMutator, randoopResults123$ConditionalsBoundaryMutator, method='spearman')
cor.test(manualResults123$NegateConditionalsMutator, manualResults123$ConditionalsBoundaryMutator, method='spearman')
```

# ConditionalsBoundaryMutator vs MathMutator
```{r}
par(mfrow = c(2,2))
plot(evoResults123$MathMutator ~ evoResults123$ConditionalsBoundaryMutator, data = evoResults123)
plot(randoopResults123$MathMutator ~ randoopResults123$ConditionalsBoundaryMutator, data = randoopResults123)
plot(manualResults123$MathMutator ~ manualResults123$ConditionalsBoundaryMutator, data = manualResults123)

cor.test(evoResults123$MathMutator, evoResults123$ConditionalsBoundaryMutator, method='spearman')
cor.test(randoopResults123$MathMutator, randoopResults123$ConditionalsBoundaryMutator, method='spearman')
cor.test(manualResults123$MathMutator, manualResults123$ConditionalsBoundaryMutator, method='spearman')
```

# ConditionalsBoundaryMutator vs InvertNegsMutator
```{r}
par(mfrow = c(2,2))
plot(evoResults123$InvertNegsMutator ~ evoResults123$ConditionalsBoundaryMutator, data = evoResults123)
plot(randoopResults123$InvertNegsMutator ~ randoopResults123$ConditionalsBoundaryMutator, data = randoopResults123)
plot(manualResults123$InvertNegsMutator ~ manualResults123$ConditionalsBoundaryMutator, data = manualResults123)

cor.test(evoResults123$InvertNegsMutator, evoResults123$ConditionalsBoundaryMutator, method='spearman')
cor.test(randoopResults123$InvertNegsMutator, randoopResults123$ConditionalsBoundaryMutator, method='spearman')
cor.test(manualResults123$InvertNegsMutator, manualResults123$ConditionalsBoundaryMutator, method='spearman')
```

## VoidMethodCallMutator

# VoidMethodCallMutator vs IncrementsMutator
```{r}
par(mfrow = c(2,2))
plot(evoResults123$IncrementsMutator ~ evoResults123$VoidMethodCallMutator, data = evoResults123)
plot(randoopResults123$IncrementsMutator ~ randoopResults123$VoidMethodCallMutator, data = randoopResults123)
plot(manualResults123$IncrementsMutator ~ manualResults123$VoidMethodCallMutator, data = manualResults123)

cor.test(evoResults123$IncrementsMutator, evoResults123$VoidMethodCallMutator, method='spearman')
cor.test(randoopResults123$IncrementsMutator, randoopResults123$VoidMethodCallMutator, method='spearman')
cor.test(manualResults123$IncrementsMutator, manualResults123$VoidMethodCallMutator, method='spearman')
```

# VoidMethodCallMutator vs NegateConditionalsMutator
```{r}
par(mfrow = c(2,2))
plot(evoResults123$NegateConditionalsMutator ~ evoResults123$VoidMethodCallMutator, data = evoResults123)
plot(randoopResults123$NegateConditionalsMutator ~ randoopResults123$VoidMethodCallMutator, data = randoopResults123)
plot(manualResults123$NegateConditionalsMutator ~ manualResults123$VoidMethodCallMutator, data = manualResults123)

cor.test(evoResults123$NegateConditionalsMutator, evoResults123$VoidMethodCallMutator, method='spearman')
cor.test(randoopResults123$NegateConditionalsMutator, randoopResults123$VoidMethodCallMutator, method='spearman')
cor.test(manualResults123$NegateConditionalsMutator, manualResults123$VoidMethodCallMutator, method='spearman')
```

# VoidMethodCallMutator vs MathMutator
```{r}
par(mfrow = c(2,2))
plot(evoResults123$MathMutator ~ evoResults123$VoidMethodCallMutator, data = evoResults123)
plot(randoopResults123$MathMutator ~ randoopResults123$VoidMethodCallMutator, data = randoopResults123)
plot(manualResults123$MathMutator ~ manualResults123$VoidMethodCallMutator, data = manualResults123)

cor.test(evoResults123$MathMutator, evoResults123$VoidMethodCallMutator, method='spearman')
cor.test(randoopResults123$MathMutator, randoopResults123$VoidMethodCallMutator, method='spearman')
cor.test(manualResults123$MathMutator, manualResults123$VoidMethodCallMutator, method='spearman')
```

# VoidMethodCallMutator vs InvertNegsMutator
```{r}
par(mfrow = c(2,2))
plot(evoResults123$InvertNegsMutator ~ evoResults123$VoidMethodCallMutator, data = evoResults123)
plot(randoopResults123$InvertNegsMutator ~ randoopResults123$VoidMethodCallMutator, data = randoopResults123)
plot(manualResults123$InvertNegsMutator ~ manualResults123$VoidMethodCallMutator, data = manualResults123)

cor.test(evoResults123$InvertNegsMutator, evoResults123$VoidMethodCallMutator, method='spearman')
cor.test(randoopResults123$InvertNegsMutator, randoopResults123$VoidMethodCallMutator, method='spearman')
cor.test(manualResults123$InvertNegsMutator, manualResults123$VoidMethodCallMutator, method='spearman')
```

## IncrementsMutator

# IncrementsMutator vs NegateConditionalsMutator
```{r}
par(mfrow = c(2,2))
plot(evoResults123$NegateConditionalsMutator ~ evoResults123$IncrementsMutator, data = evoResults123)
plot(randoopResults123$NegateConditionalsMutator ~ randoopResults123$IncrementsMutator, data = randoopResults123)
plot(manualResults123$NegateConditionalsMutator ~ manualResults123$IncrementsMutator, data = manualResults123)

cor.test(evoResults123$NegateConditionalsMutator, evoResults123$IncrementsMutator, method='spearman')
cor.test(randoopResults123$NegateConditionalsMutator, randoopResults123$IncrementsMutator, method='spearman')
cor.test(manualResults123$NegateConditionalsMutator, manualResults123$IncrementsMutator, method='spearman')
```

# IncrementsMutator vs MathMutator
```{r}
par(mfrow = c(2,2))
plot(evoResults123$MathMutator ~ evoResults123$IncrementsMutator, data = evoResults123)
plot(randoopResults123$MathMutator ~ randoopResults123$IncrementsMutator, data = randoopResults123)
plot(manualResults123$MathMutator ~ manualResults123$IncrementsMutator, data = manualResults123)

cor.test(evoResults123$MathMutator, evoResults123$IncrementsMutator, method='spearman')
cor.test(randoopResults123$MathMutator, randoopResults123$IncrementsMutator, method='spearman')
cor.test(manualResults123$MathMutator, manualResults123$IncrementsMutator, method='spearman')
```

# IncrementsMutator vs InvertNegsMutator
```{r}
par(mfrow = c(2,2))
plot(evoResults123$InvertNegsMutator ~ evoResults123$IncrementsMutator, data = evoResults123)
plot(randoopResults123$InvertNegsMutator ~ randoopResults123$IncrementsMutator, data = randoopResults123)
plot(manualResults123$InvertNegsMutator ~ manualResults123$IncrementsMutator, data = manualResults123)

cor.test(evoResults123$InvertNegsMutator, evoResults123$IncrementsMutator, method='spearman')
cor.test(randoopResults123$InvertNegsMutator, randoopResults123$IncrementsMutator, method='spearman')
cor.test(manualResults123$InvertNegsMutator, manualResults123$IncrementsMutator, method='spearman')
```

## NegateConditionalsMutator

# NegateConditionalsMutator vs MathMutator
```{r}
par(mfrow = c(2,2))
plot(evoResults123$MathMutator ~ evoResults123$NegateConditionalsMutator, data = evoResults123)
plot(randoopResults123$MathMutator ~ randoopResults123$NegateConditionalsMutator, data = randoopResults123)
plot(manualResults123$MathMutator ~ manualResults123$NegateConditionalsMutator, data = manualResults123)

cor.test(evoResults123$MathMutator, evoResults123$NegateConditionalsMutator, method='spearman')
cor.test(randoopResults123$MathMutator, randoopResults123$NegateConditionalsMutator, method='spearman')
cor.test(manualResults123$MathMutator, manualResults123$NegateConditionalsMutator, method='spearman')
```

# NegateConditionalsMutator vs InvertNegsMutator
```{r}
par(mfrow = c(2,2))
plot(evoResults123$InvertNegsMutator ~ evoResults123$NegateConditionalsMutator, data = evoResults123)
plot(randoopResults123$InvertNegsMutator ~ randoopResults123$NegateConditionalsMutator, data = randoopResults123)
plot(manualResults123$InvertNegsMutator ~ manualResults123$NegateConditionalsMutator, data = manualResults123)

cor.test(evoResults123$InvertNegsMutator, evoResults123$NegateConditionalsMutator, method='spearman')
cor.test(randoopResults123$InvertNegsMutator, randoopResults123$NegateConditionalsMutator, method='spearman')
cor.test(manualResults123$InvertNegsMutator, manualResults123$NegateConditionalsMutator, method='spearman')
```

## MathMutator

# MathMutator vs InvertNegsMutator
```{r}
par(mfrow = c(2,2))
plot(evoResults123$InvertNegsMutator ~ evoResults123$MathMutator, data = evoResults123)
plot(randoopResults123$InvertNegsMutator ~ randoopResults123$MathMutator, data = randoopResults123)
plot(manualResults123$InvertNegsMutator ~ manualResults123$MathMutator, data = manualResults123)

cor.test(evoResults123$InvertNegsMutator, evoResults123$MathMutator, method='spearman')
cor.test(randoopResults123$InvertNegsMutator, randoopResults123$MathMutator, method='spearman')
cor.test(manualResults123$InvertNegsMutator, manualResults123$MathMutator, method='spearman')
```
