---
title: Exploring Nondeterminism in Tools That Automatically Generate or Analyse Test
  Suites
author: "Beatriz Souza"
date: "5/14/2019"
output:
  html_document: default
  pdf_document: default
---

# Installing and loading packages
```{r}
install.packages("ggpubr")
install.packages("ggplot2")
install.packages("reshape")
install.packages("reshape2")
install.packages("dplyr")
library("ggplot2")
library("reshape")
library("reshape2")
library("ggpubr")
library("dplyr")
```

# Reading data
```{r}
evo <- read.csv('/home/beatriz/Documents/SRC-2019/statistics/exploringNondeterminism/evo1Execution.csv', sep = ",", header = TRUE)
evoMelted <- melt(evo, id = c("Project", "Tool"))
#evoMelted

randoop <- read.csv('/home/beatriz/Documents/SRC-2019/statistics/exploringNondeterminism/randoop1Execution.csv', sep = ",", header = TRUE)
randoopMelted <- melt(randoop, id = c("Project", "Tool"))
#randoopMelted

pitEvo <- read.csv('/home/beatriz/Documents/SRC-2019/statistics/exploringNondeterminism/pitSameProjectSameTestSuiteEvo.csv', sep = ",", header = TRUE)
pitEvoMelted <- melt(pitEvo, id = c("Project", "Tool"))
#pitEvoMelted

pitRandoop <- read.csv('/home/beatriz/Documents/SRC-2019/statistics/exploringNondeterminism/pitSameProjectSameTestSuiteRandoop.csv', sep = ",", header = TRUE)
pitRandoopMelted <- melt(pitRandoop, id = c("Project", "Tool"))
#pitRandoopMelted

pitManual <- read.csv('/home/beatriz/Documents/SRC-2019/statistics/exploringNondeterminism/pitSameProjectSameTestSuiteManual.csv', sep = ",", header = TRUE)
pitManualMelted <- melt(pitManual, id = c("Project", "Tool"))
#pitManualMelted
```

## Declaring common values
```{r}
projects=c("BCEL","CLI","Codec", "CSV", "Email", "File\nUpload", "Imaging", "Lang", "Statistics", "Validator")
```

## PIT was executed once for each test suite.

# Here we analyse the difference between test suites generated for the same project with EvoSuite in terms of line and mutation coverage. 
```{r}
ggplot(data = evoMelted, aes(x=Project, y=value)) +
  geom_boxplot(aes(fill=variable)) +
  scale_x_discrete(labels=projects) + 
  labs(x ="Project", y = "Value") +
  scale_fill_manual(values = c("#f0f0f0", "#636363"), name = "Coverage", 
                    labels = c("Line", "Mutation"))

# Line Coverage mean, variation and standard deviation
evoMeanVariationSDLC <- evo %>% group_by(Project) %>% summarise(LineCoverageAverage = mean(LineCoverage),
                                                              LineCoverageVariation = var(LineCoverage),
                                                              LineCoverageStandardDeviation = sd(LineCoverage))
evoMeanVariationSDLC

# Mutation Coverage mean, variation and standard deviation
evoMeanVariationSDMC <- evo %>% group_by(Project) %>% summarise(MutationCoverageAverage = mean(MutationCoverage),
                                                              MutationCoverageVariation = var(MutationCoverage),
                                                              MutationCoverageStandardDeviation = sd(MutationCoverage))
evoMeanVariationSDMC
```

# Here we analyse the difference between test suites generated for the same project with Randoop in terms of line and mutation coverage. 
```{r}
ggplot(data = randoopMelted, aes(x=Project, y=value)) +
  geom_boxplot(aes(fill=variable)) +
  scale_x_discrete(labels=projects) + 
  labs(x ="Project", y = "Value") +
  scale_fill_manual(values = c("#f0f0f0", "#636363"), name = "Coverage", 
                    labels = c("Line", "Mutation"))

# Line Coverage mean, variation and standard deviation
randoopMeanVariationSDLC <- randoop %>% group_by(Project) %>% summarise(LineCoverageAverage = mean(LineCoverage),
                                                              LineCoverageVariation = var(LineCoverage),
                                                              LineCoverageStandardDeviation = sd(LineCoverage))
randoopMeanVariationSDLC

# Mutation Coverage mean, variation and standard deviation
randoopMeanVariationSDMC <- randoop %>% group_by(Project) %>% summarise(MutationCoverageAverage = mean(MutationCoverage),
                                                              MutationCoverageVariation = var(MutationCoverage),
                                                              MutationCoverageStandardDeviation = sd(MutationCoverage))
randoopMeanVariationSDMC
```

# Here we compare the standard deviations of line and mutation coverage of the test suites generated with EvoSuite and Randoop.
```{r}
# Line Coverage
wilcox.test(evoMeanVariationSDLC$LineCoverageStandardDeviation, randoopMeanVariationSDLC$LineCoverageStandardDeviation, paired = TRUE)

# Mutation Coverage
wilcox.test(evoMeanVariationSDMC$MutationCoverageStandardDeviation, randoopMeanVariationSDMC$MutationCoverageStandardDeviation, paired = TRUE)
```

## PIT was executed 10 times for each test suite.

# Here we analyse PIT's outputs when executed for the same project and the same test suites

# EvoSuite
```{r}
ggplot(data = pitEvoMelted, aes(x=Project, y=value)) +
  geom_boxplot(aes(fill=variable)) +
  scale_x_discrete(labels=projects) + 
  labs(x = "Project", y = "Value") +
  scale_fill_manual(values = c("#f0f0f0", "#636363"), name = "Coverage", 
                    labels = c("Line", "Mutation"))
```

# Randoop
```{r}
ggplot(data = pitRandoopMelted, aes(x=Project, y=value)) +
  geom_boxplot(aes(fill=variable)) +
  scale_x_discrete(labels=projects) + 
  labs(x ="Project", y = "Value") +
  scale_fill_manual(values = c("#f0f0f0", "#636363"), name = "Coverage", 
                    labels = c("Line", "Mutation"))
```

# Manual
```{r}
ggplot(data = pitManualMelted, aes(x=Project, y=value)) +
  geom_boxplot(aes(fill=variable)) +
  scale_x_discrete(labels=projects) + 
  labs(x ="Project", y = "Value") +
  scale_fill_manual(values = c("#f0f0f0", "#636363"), name = "Coverage", 
                    labels = c("Line", "Mutation"))
```
