---
title: Which Unit Test Generation Method is Better? A Comparison Through Different
  Mutation Operators
author: "Beatriz Souza"
date: "6/4/2019"
output: html_document
---

## Installing and loading packages
```{r}
install.packages("ggpubr")
install.packages("ggplot2")
install.packages("reshape")
install.packages("reshape2")
install.packages("dplyr")
library("ggplot2")
library("reshape")
library("reshape2")
library("ggpubr")
library("dplyr")
```

## Reading data
```{r}
evoResults1 <- read.csv('/home/beatriz/Desktop/FinaldataSet/evoResultsEvoAvg.csv', sep = ",", header = TRUE)
evoResults2 <- read.csv('/home/beatriz/Desktop/FinaldataSet/evoResults2EvoAvg.csv', sep = ",", header = TRUE)
evoResults3 <- read.csv('/home/beatriz/Desktop/FinaldataSet/evoResults3EvoAvg.csv', sep = ",", header = TRUE)

randoopResults1 <- read.csv('/home/beatriz/Desktop/FinaldataSet/randoopResultsRandoopAvg.csv', sep = ",", header = TRUE)
randoopResults2 <- read.csv('/home/beatriz/Desktop/FinaldataSet/randoopResults2RandoopAvg.csv', sep = ",", header = TRUE)
randoopResults3 <- read.csv('/home/beatriz/Desktop/FinaldataSet/randoopResults3RandoopAvg.csv', sep = ",", header = TRUE)

manualResults1 <- read.csv('/home/beatriz/Desktop/FinaldataSet/manualSuitesResultsPITAvg.csv', sep = ",", header = TRUE)
manualResults2 <- read.csv('/home/beatriz/Desktop/FinaldataSet/manualSuitesResults2PITAvg.csv', sep = ",", header = TRUE)
manualResults3 <- read.csv('/home/beatriz/Desktop/FinaldataSet/manualSuitesResults3PITAvg.csv', sep = ",", header = TRUE)
```

## Merging data
```{r}
evoResults12 <- merge(evoResults1, evoResults2, all = TRUE)
#evo12
evoResults123 <- merge(evoResults12, evoResults3, all = TRUE)
#evoResults123

randoopResults12 <- merge(randoopResults1, randoopResults2, all = TRUE)
#randoopResults12
randoopResults123 <- merge(randoopResults12, randoopResults3, all = TRUE)
#randoopResults123

manualResults12 <- merge(manualResults1, manualResults2, all = TRUE)
#manualResults12
manualResults123 <- merge(manualResults12, manualResults3, all = TRUE)
#manualResults123

evoAndRandoopDataSet <- merge(evoResults123, randoopResults123, all = TRUE)
completeDataSet <- merge(evoAndRandoopDataSet, manualResults123, all = TRUE)
#completeDataSet
```

## Declaring common values
```{r}
metrics1 = c("LineCoverage","MutationCoverage")
metrics2 = c("ReturnValsMutator","ConditionalsBoundaryMutator",
             "VoidMethodCallMutator","IncrementsMutator",
             "NegateConditionalsMutator","MathMutator", "InvertNegsMutator")

projects=c("BCEL","CLI","Codec", "CSV", "Email", "FileUpload", "Imaging", "Lang", "Statistics", "Validator")
```

## Melting data
```{r}
completeDataSet.m1 <- melt(completeDataSet, id.var = "Tool", measure.vars = metrics1)
#completeDataSet.m1

completeDataSet.m2 <- melt(completeDataSet, id.var = "Tool", measure.vars = metrics2)
#completeDataSet.m2

completeDataSet.m3 <- melt(completeDataSet, id.vars = c("Tool", "Project"))
#completeDataSet.m3
```


## Ploting Box-plots
# Line Coverage and Mutation Coverage
```{r}
ggplot(data = completeDataSet.m1, aes(x=variable, y=value)) +
  geom_boxplot(aes(fill=Tool)) +
  scale_x_discrete(labels= c("LineCoverage", "MutationCoverage"))
```

# PIT's Default Mutation Operators
```{r}
ggplot(data = completeDataSet.m2, aes(x=variable, y=value)) +
  geom_boxplot(aes(fill=Tool)) +
  scale_x_discrete(labels= c(
             "RVM","CBM",
             "VMCM","IM",
             "NCM","MM", "INM"))
```

### Line Coverage
## Comparing Line Coverage per Tool
```{r}
# If paired = FALSE, you perform a Mann-Whitney test
wilcox.test(manualResults123$LineCoverage, evoResults123$LineCoverage, paired = TRUE, alternative = "greater")
wilcox.test(manualResults123$LineCoverage, randoopResults123$LineCoverage, paired = TRUE, alternative = "greater")
wilcox.test(evoResults123$LineCoverage, randoopResults123$LineCoverage, paired = TRUE, alternative = "greater")
```

### Mutation Coverage
## Comparing Mutation Coverage per Tool
```{r}
wilcox.test(manualResults123$MutationCoverage, evoResults123$MutationCoverage,  paired = TRUE, alternative = "greater")
wilcox.test(manualResults123$MutationCoverage, randoopResults123$MutationCoverage,  paired = TRUE, alternative = "greater")
wilcox.test(evoResults123$MutationCoverage, randoopResults123$MutationCoverage, paired = TRUE, alternative = "greater")
```

### Mutation Operators
## Comparing ReturnValsMutator Coverage per Tool
```{r}
wilcox.test(manualResults123$ReturnValsMutator, evoResults123$ReturnValsMutator, paired = TRUE, alternative = "greater")
wilcox.test(manualResults123$ReturnValsMutator, randoopResults123$ReturnValsMutator,  paired = TRUE, alternative = "greater")
wilcox.test(evoResults123$ReturnValsMutator, randoopResults123$ReturnValsMutator, paired = TRUE, alternative = "greater")
wilcox.test(evoResults123$ReturnValsMutator, randoopResults123$ReturnValsMutator, paired = TRUE)
```

## Comparing ConditionalsBoundaryMutator Coverage per Tool
```{r}
wilcox.test(manualResults123$ConditionalsBoundaryMutator, evoResults123$ConditionalsBoundaryMutator, paired = TRUE, alternative = "greater")
wilcox.test(manualResults123$ConditionalsBoundaryMutator, randoopResults123$ConditionalsBoundaryMutator, paired = TRUE, alternative = "greater")
wilcox.test(evoResults123$ConditionalsBoundaryMutator, randoopResults123$ConditionalsBoundaryMutator, paired = TRUE, alternative = "greater")
```

## Comparing VoidMethodCallMutator Coverage per Tool
```{r}
wilcox.test(manualResults123$VoidMethodCallMutator, evoResults123$VoidMethodCallMutator, paired = TRUE, alternative = "greater")
wilcox.test(manualResults123$VoidMethodCallMutator, randoopResults123$VoidMethodCallMutator, paired = TRUE, alternative = "greater")
wilcox.test(evoResults123$VoidMethodCallMutator, randoopResults123$VoidMethodCallMutator, paired = TRUE, alternative = "greater")
wilcox.test(randoopResults123$VoidMethodCallMutator, evoResults123$VoidMethodCallMutator, paired = TRUE, alternative = "greater")
wilcox.test(randoopResults123$VoidMethodCallMutator, evoResults123$VoidMethodCallMutator, paired = TRUE)
```

## Comparing IncrementsMutator Coverage per Tool
```{r}
wilcox.test(manualResults123$IncrementsMutator, evoResults123$IncrementsMutator, paired = TRUE, alternative = "greater")
wilcox.test(manualResults123$IncrementsMutator, randoopResults123$IncrementsMutator, paired = TRUE, alternative = "greater")
wilcox.test(evoResults123$IncrementsMutator, randoopResults123$IncrementsMutator, paired = TRUE, alternative = "greater")
wilcox.test(evoResults123$IncrementsMutator, randoopResults123$IncrementsMutator, paired = TRUE)
```

## Comparing NegateConditionalsMutator Coverage per Tool
```{r}
wilcox.test(manualResults123$NegateConditionalsMutator, evoResults123$NegateConditionalsMutator, paired = TRUE, alternative = "greater")
wilcox.test(manualResults123$NegateConditionalsMutator, randoopResults123$NegateConditionalsMutator, paired = TRUE, alternative = "greater")
wilcox.test(evoResults123$NegateConditionalsMutator, randoopResults123$NegateConditionalsMutator, paired = TRUE, alternative = "greater")

```

## Comparing MathMutator Coverage per Tool
```{r}
wilcox.test(manualResults123$MathMutator, evoResults123$MathMutator, paired = TRUE, alternative = "greater")
wilcox.test(manualResults123$MathMutator, randoopResults123$MathMutator, paired = TRUE, alternative = "greater")
wilcox.test(evoResults123$MathMutator, randoopResults123$MathMutator, paired = TRUE, alternative = "greater")
```
  
## Comparing InvertNegsMutator Coverage per Tool
```{r}
evoResults123WithoutNA <- evoResults123 %>% select(InvertNegsMutator) %>% filter(!is.na(InvertNegsMutator))
#evoResults123WithoutNA
randoopResults123WithoutNA <- randoopResults123 %>% select(InvertNegsMutator) %>% filter(!is.na(InvertNegsMutator))
#randoopResults123WithoutNA
manualResults123WithoutNA <- manualResults123 %>% select(InvertNegsMutator) %>% filter(!is.na(InvertNegsMutator))
#manualResults123WithoutNA

wilcox.test(manualResults123WithoutNA$InvertNegsMutator, evoResults123WithoutNA$InvertNegsMutator, paired = TRUE, alternative = "greater")
wilcox.test(manualResults123WithoutNA$InvertNegsMutator, randoopResults123WithoutNA$InvertNegsMutator, paired = TRUE, alternative = "greater")
wilcox.test(evoResults123WithoutNA$InvertNegsMutator, randoopResults123WithoutNA$InvertNegsMutator, paired = TRUE, alternative = "greater")

wilcox.test(manualResults123WithoutNA$InvertNegsMutator, evoResults123WithoutNA$InvertNegsMutator, paired = TRUE)
wilcox.test(manualResults123WithoutNA$InvertNegsMutator, randoopResults123WithoutNA$InvertNegsMutator, paired = TRUE)
wilcox.test(evoResults123WithoutNA$InvertNegsMutator, randoopResults123WithoutNA$InvertNegsMutator, paired = TRUE)
```

